Introducing ICBe: Supplementary Information

### 2024-06-16 replication_paper/psrm_draft/ICBe_supplemental_information.Rmd
pre-pull

#oh is it because break is reserved in R? lol
#icb_crises <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb1v14.csv")) %>% janitor::clean_names()
icb_crises  <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) %>% janitor::clean_names()
icb_crises$start_simple <- icb_crises$yrtrig+(icb_crises$motrig/12)
icb_crises$end_simple <- icb_crises$yrterm+(icb_crises$moterm/12)

#somehow break of all things is a b roken name
#icb_actors <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb2v14.csv"))
icb_actors <- read.csv(paste0(here::here(), "/replication_data/in/icb2v14.csv"))

@@

#The answer is I have to include it as an image, none of the table options were compiling correctly without error
#,  ft.arraystretch=0.75

temp_all <-  ICBe_crises_markdown %>% ungroup() %>% dplyr::select(
                    crisno, crisis_text,  yrtrig , yrterm,  n_sentence_number_int_aligned, n_events, 
                    coders_expert , 
                    coders_novice ,
                    actors , 
                    units_domains, 
                    forces_fatalities
                    ) %>%
              mutate_all(as.character) %>%
              mutate(crisis_text = crisis_text %>% stringr::str_to_title() %>% str_replace("Ii$","II"))

convert_to_ft <- function(x){
     x %>% flextable::as_flextable() %>%
      flextable::set_header_labels(values =
          list(crisno = "#",
                crisis_text = "Title",
                yrtrig = "Start",
                yrterm = "End",
                n_sentence_number_int_aligned = "Sent.",
                n_events = "Events",
                coders_expert = "Exp.",
                coders_novice = "Nov.",
                actors = "Actors",
                units_domains = "Units/Domains",
                forces_fatalities = "Forces/Fatalities"
                #value_markdown = "Abstract"
               ) ) %>%
      flextable::add_header(values =
          list(crisno = "Crisis",
                crisis_text = "Crisis",
                yrtrig = "Years",
                yrterm = "Years",
                n_sentence_number_int_aligned = "Counts",
                n_events = "Counts",
                coders_expert = "Coders",
                coders_novice = "Coders"#,
                #value_markdown = "Abstract"
               ) ) %>%
      flextable::merge_h(part = "header" ) %>%
      flextable::width( j = 1, width=0.3)  %>%
      flextable::width( j = 2, width=2.75)  %>%
      flextable::width( j = 3, width=0.6)  %>%
      flextable::width( j = 4, width=0.6)  %>%
      flextable::width( j = 5, width=0.25)  %>%
      flextable::width( j = 6, width=0.25)  %>%
      flextable::width( j = 7, width=0.25)  %>%
      flextable::width( j = 8, width=0.35)  %>%
      flextable::width( j = 9, width=2.5)  %>%
      flextable::width( j = 10, width=1.5)  %>%
      flextable::width( j = 11, width=1.0)  %>%
      flextable::fontsize(size = 9, part = "all") %>%
      flextable::padding(padding = 0.1, part = "all") %>%
      flextable::line_spacing(space = 1, part = "body") %>%
      flextable::bg( i = which( 1:nrow(x) %% 2 == 1)  , part = "body", bg = "#EFEFEF") %>%
      ftExtra::colformat_md(j = 9:11, part="body")
}

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft1.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft2.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft3.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft4.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft5.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft6.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft7.png"), zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:480) ) %>% convert_to_ft()  %>% 
  save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft8.png"), zoom=1)

@@

# writeLines(icb_text$sentence %>% na.omit() %>% iconv("UTF-8", "ASCII", "?"), paste0(here::here(), "/replication_data/temp/sentences.txt"), useBytes = T)

fromscratch=F
if(fromscratch){
  #Here we use spacy to extract verbs from the sentences
  p_load("spacyr")
  #spacy_install() 
  spacy_initialize(model = "en_core_web_sm")

@@

#wordnet rdf (in tripple format)
#wordnet rdf (in tripple format)
fromscratch=F

@@

verbs_sentence_wordnet <- verbs_sentence %>% left_join(wordnet_verbs)
#oh got it this is all possible matching glosses per ICBe sentence
#dim(verbs_sentence_wordnet) #227,426

#I think we use sbert to embed the original sentence and the gloss and then calculate pairwise distances

@@

```{r}
 # py_install("tqdm")
 # py_install("pandas")
 # py_install("transformers")
```

@@

# can install python packages in R using code chunk above

fromscratch=False

if fromscratch:
  import torch
  use_cuda = torch.cuda.is_available()
  if use_cuda:
      print('__CUDNN VERSION:', torch.backends.cudnn.version())
      print('__Number CUDA Devices:', torch.cuda.device_count())
      print('__CUDA Device Name:',torch.cuda.get_device_name(0))
      print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(0).total_memory/1e9)
      print('__CUDA Device Name:',torch.cuda.get_device_name(1))
      print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(1).total_memory/1e9)    
  import random
  import os
  from tqdm.auto import tqdm
  import pandas as pd
  from transformers import pipeline
  from transformers.pipelines.pt_utils import KeyDataset
  from sentence_transformers import SentenceTransformer
  import numpy as np
  glosses=np.array(r.gloss_unique) #sentences_unique_sanitized
  glosses_chars = np.array([len(q) for q in glosses])
  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
  len(glosses) #4977
  n=len(glosses)
  chunk_length=100
  n_chunks = int(np.ceil(n/chunk_length)) #can only 
  glosses_chunks=[glosses[i:i + chunk_length] for i in range(0, n, chunk_length)]
  len(glosses_chunks)
  len(glosses_chunks[0])  
  model = SentenceTransformer('paraphrase-mpnet-base-v2')
  glosses_embeddings = np.vstack([model.encode(q) for q in glosses_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
  glosses_embeddings.shape #(4977, 768)
else:
  print("Skipping")

```{python embed sentences for wordnet , echo=F, results='hide', message=F, warning=F, eval=T , cache=F}

#Make sure you have a gpu if you want to run thi

@@

fromscratch=False
if fromscratch:
  from sentence_transformers import SentenceTransformer
  import numpy as np
  sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
  sentence_chars = np.array([len(q) for q in sentences])
  #sentences=sentences[sentence_chars<1000] #cull anything with too many characters
  len(sentences) #12161 12162
  n=len(sentences)
  chunk_length=100
  n_chunks = int(np.ceil(n/chunk_length)) #can only 
  sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
  len(sentences_chunks)
  len(sentences_chunks[0])  
  #model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
  #model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
  model = SentenceTransformer('paraphrase-mpnet-base-v2')
  #sentences
  #sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
  #temp = model.encode(sentences_chunks[0])
  sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
  sentences_embeddings.shape #(12103, 768)
else:
  print("Skipping")

@@

fromsrcatch=F
if(fromsrcatch){
  #py$sentences
  #py$glosses
  glosses_embeddings <- py$glosses_embeddings
  sentences_embeddings <- py$sentences_embeddings

@@

  condition_glosses_embeddings <- verbs_sentence_wordnet$gloss %in% rownames(glosses_embeddings)
  table(condition_glosses_embeddings) #there are 130 glosses that aren't in there
  gloss_clean <- verbs_sentence_wordnet$gloss
  gloss_clean[!condition_glosses_embeddings] <- rownames(glosses_embeddings)[1] #just a placeholder need to kill after
  glosses_embeddings_expanded <- glosses_embeddings[gloss_clean ,]
  dim(glosses_embeddings_expanded)

  condition_sentences_embeddings <- verbs_sentence_wordnet$sentence %in% rownames(sentences_embeddings)
  table(condition_sentences_embeddings) #all are in it
  sentences_clean <- verbs_sentence_wordnet$sentence
  sentences_clean[!condition_sentences_embeddings] <- rownames(sentences_embeddings)[1] #just a placeholder need to kill after
  sentences_embeddings_expanded <- sentences_embeddings[sentences_clean ,]
  dim(sentences_embeddings_expanded)

  #Isn't it just one minus the other?
  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))

} else {

  verbs_sentence_wordnet <- readRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))

@@

        #bg( j = condition, part = "body", bg = "#EFEFEF") %>%
        #width(j = 1, width=1.25) %>%
        #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
        flextable::fontsize(size = 6, part = "all") %>% 
        #rotate(rotation="tbrl",part="header") %>%
        set_header_labels( values = list(lemma = "lemma", wordnetid = "wordnetid", gloss="gloss", n="uses")) %>%
        #align(align = "center", part = "body") %>%
        #align(align = "center", part = "header") %>%
        flextable::padding(padding = 0, part = "all") %>%
        flextable::line_spacing(space = 1, part = "body") %>%
        #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
        #fit_to_width(max_width=12) #This is crazy slow
        #flextable::autofit() 
        #set_table_properties(width = 1, layout = "autofit")

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}

fromscratch=F
if(fromscratch){
  means_group_any <- codings_long_agreement %>% filter(value_normalized!='') %>% 
                     #filter(votes_total>1) %>% #
                     group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
                     dplyr::select(Experts=percent_expert,Novices=percent_novice) %>% summarise_all(mean)

@@

  means_keap <- codings_long_agreement %>% 
                #Algo 1 agreement
                filter(algo1==1) %>% 
                #This is top 1 agreement
                filter(value_normalized!='') %>% group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
                group_by(varname_normalized) %>%
                #filter(votes_total>1) %>% #What work is this doing?
                #filter(selected_by_experts>=1) %>%
                dplyr::select(Experts_keep=percent_expert,Novices_keep=percent_novice) %>% summarise_all(mean, na.rm=T)

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_percent_chose_tag_by_concept.png'), 
                  plot = p_percent_chose_tag_by_concept, width=8, height=8)
}

@@

fromscratch=F
if(fromscratch){
  raterconfidence <- icb_long_clean %>% filter(email_id %>% str_detect('expert') & varname_normalized=='raterconfidence' ) %>%
                     dplyr::select(email_id, crisno, sentence_number_int_aligned, raterconfidence=value_normalized) %>% distinct()

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_percent_chose_tag_by_confidence.png'), 
                  plot = p_percent_chose_tag_by_confidence, width=8, height=6)
}

@@

# Recall
\hphantom{em}

## Synthetic Narratives
\hphantom{em}

@@

cuba_recall <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing", 
                                sheet="final") %>% janitor::clean_names()

replace_emoticons_cuba <- function(x){
  x %>% str_replace_all('\U0001f1e8\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")) %>%
        #https://emojiterra.com/flag-for-united-states/
        str_replace_all('\U0001f1fa\U0001f1f8',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
        #https://emojiterra.com/flag-for-russia/
        str_replace_all('\U0001f1f7\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15180.png) ")) %>% 
        #Turkey
        str_replace_all('\U0001f1f9\U0001f1f7',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q43.png) ")) %>% 
        #U.N.
        str_replace_all('\U0001f1fa\U0001f1f3',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q1065.png) "))
}

ft_cuba_recall<- cuba_recall %>% 
                            dplyr::select(date, event, documents, icb_narrative, icbe=ic_be, icb, mids, phoenix_2)  %>%
                            mutate(event = event %>% replace_emoticons_cuba() ) %>%
                            flextable::as_flextable() %>%
                            flextable::set_header_labels(values =
                            list(
                                  event = "Event",
                                  documents = "Mentions",
                                  icb_narrative = "ICB Narrative",
                                  icbe = "ICBe",
                                  icb = "ICB",
                                  mids="MIDs",
                                  phoenix_2="Phoenix"
                                 ) ) %>%
                            flextable::width( j = 1, width=0.25)  %>% 
                            flextable::width( j =2, width=2.0)  %>% 
                            flextable::width( j = 6:8, width=2.0)  %>% 
                            flextable::fontsize(size = 7, part = "all") %>%
                            #valign(j = 1:3, valign = "top", part = "body") %>%
                            flextable::line_spacing( space = 1.0, part = "all") %>% 
                            padding( padding = 1, part = "all") %>% 
                            bg( i = which( (1:nrow(cuba_recall) %% 2)==1   ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                            ftExtra::colformat_md(j = 2, part="body")

@@

crimea_recall <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1YesAx1CkYCgrEi_WVJ9aho60HesWA6p-3XMma9IzBrI/edit?usp=sharing", 
                                sheet="final") %>% janitor::clean_names()

>>>>

#icb_crises <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb1v14.csv")) %>% janitor::clean_names()
icb_crises  <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) %>% janitor::clean_names()
icb_crises$start_simple <- icb_crises$yrtrig+(icb_crises$motrig/12)
icb_crises$end_simple <- icb_crises$yrterm+(icb_crises$moterm/12)

#icb_actors <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb2v14.csv"))
icb_actors <- read.csv(paste0(here::here(), "/replication_data/in/icb2v14.csv"))

@@

temp_all <-  ICBe_crises_markdown %>% ungroup() %>% dplyr::select(
                    crisno, crisis_text,  yrtrig , yrterm,  n_sentence_number_int_aligned, n_events, 
                    coders_expert , 
                    coders_novice ,
                    actors , 
                    units_domains, 
                    forces_fatalities
                    ) %>%
  mutate_all(as.character) %>%
  mutate(crisis_text = crisis_text %>% stringr::str_to_title() %>% str_replace("Ii$","II")) %>%
  dplyr::mutate(actors = actors %>% stringr::str_replace_all(stringr::fixed("/home/tlscherer/Desktop/ICBEdataset/replication_data/in/"), stringr::fixed(""))) %>%
  dplyr::mutate(actors = actors %>% stringr::str_replace_all(stringr::fixed("Columbia;Cuba;Mexico;United States;Uruguay"), stringr::fixed("![](flags_small//Q739.png);![](flags_small//Q241.png);![](flags_small//Q96.png)"))) %>%
  dplyr::mutate(actors = actors %>% stringr::str_replace_all(stringr::fixed("Belgium;France;Germany;Italy;United Kingdom"), stringr::fixed(""))) %>%
  dplyr::mutate(actors = actors %>% stringr::str_replace_all(stringr::fixed("France;United Kingdom"), stringr::fixed(""))) %>%
  dplyr::mutate(actors = actors %>% stringr::str_replace_all(stringr::fixed(";Soviet Union;United States of America"), stringr::fixed(""))) %>%
  dplyr::mutate(actors = actors %>% stringr::str_replace_all(stringr::fixed(";Saudi Arabia"), stringr::fixed(""))) %>%
  dplyr::mutate(units_domains = units_domains %>% stringr::str_replace_all(stringr::fixed("/home/tlscherer/Desktop/ICBEdataset/replication_data/in/"), stringr::fixed(""))) %>%
  dplyr::mutate(forces_fatalities = forces_fatalities %>% stringr::str_replace_all(stringr::fixed("/home/tlscherer/Desktop/ICBEdataset/replication_data/in/"), stringr::fixed("")))
## DOUBLE CHECK ABOVE

convert_to_ft <- function(x){
     x %>% flextable::as_flextable() %>%
      flextable::set_header_labels(values =
          list(crisno = "#",
                crisis_text = "Title",
                yrtrig = "Start",
                yrterm = "End",
                n_sentence_number_int_aligned = "Sent.",
                n_events = "Events",
                coders_expert = "Exp.",
                coders_novice = "Nov.",
                actors = "Actors",
                units_domains = "Units/Domains",
                forces_fatalities = "Forces/Fatalities"
                #value_markdown = "Abstract"
               ) ) %>%
      flextable::add_header(values =
          list(crisno = "Crisis",
                crisis_text = "Crisis",
                yrtrig = "Years",
                yrterm = "Years",
                n_sentence_number_int_aligned = "Counts",
                n_events = "Counts",
                coders_expert = "Coders",
                coders_novice = "Coders"
                #value_markdown = "Abstract"
               ) ) %>%
      flextable::merge_h(part = "header" ) %>%
      flextable::width( j = 1, width=0.3)  %>%
      flextable::width( j = 2, width=2.75)  %>%
      flextable::width( j = 3, width=0.6)  %>%
      flextable::width( j = 4, width=0.6)  %>%
      flextable::width( j = 5, width=0.25)  %>%
      flextable::width( j = 6, width=0.25)  %>%
      flextable::width( j = 7, width=0.25)  %>%
      flextable::width( j = 8, width=0.35)  %>%
      flextable::width( j = 9, width=2.5)  %>%
      flextable::width( j = 10, width=1.5)  %>%
      flextable::width( j = 11, width=1.0)  %>%
      flextable::fontsize(size = 9, part = "all") %>%
      flextable::padding(padding = 0.1, part = "all") %>%
      flextable::line_spacing(space = 1, part = "body") %>%
      flextable::bg( i = which( 1:nrow(x) %% 2 == 1)  , part = "body", bg = "#EFEFEF") %>%
      ftExtra::colformat_md(j = 9:11, part="body")
}
```

```{r}
## Double Check Below

crisis_text_counts_ft1 <- temp_all %>% ungroup() %>% filter(crisno %in% c(1:60)) %>% convert_to_ft() 
#crisis_text_counts_ft1 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft1.png"), zoom=1)
crisis_text_counts_ft1

crisis_text_counts_ft2 <- temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  
#crisis_text_counts_ft2 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft2.png"), zoom=1)
crisis_text_counts_ft2

crisis_text_counts_ft3 <- temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft() 
#crisis_text_counts_ft3 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft3.png"), zoom=1)
crisis_text_counts_ft3

crisis_text_counts_ft4 <- temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()
#crisis_text_counts_ft4 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft4.png"), zoom=1)
crisis_text_counts_ft4

crisis_text_counts_ft5 <- temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft() 
#crisis_text_counts_ft5 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft5.png"), zoom=1)
crisis_text_counts_ft5

crisis_text_counts_ft6 <- temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft() 
#crisis_text_counts_ft6 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft6.png"), zoom=1)
crisis_text_counts_ft6

crisis_text_counts_ft7 <- temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft() 
#crisis_text_counts_ft7 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft7.png"), zoom=1)
crisis_text_counts_ft7

crisis_text_counts_ft8 <- temp_all %>% ungroup() %>% filter(crisno %in% c(421:480) ) %>% convert_to_ft() 
#crisis_text_counts_ft8 %>% save_as_image(path=here::here("replication_paper", "psrm_draft", "crisis_text_counts_ft8.png"), zoom=1)
crisis_text_counts_ft8
```

@@

# writeLines(icb_text$sentence %>% na.omit() %>% iconv("UTF-8", "ASCII", "?"), paste0(here::here(), "/replication_data/temp/sentences.txt"), useBytes = T)
fromscratch=FALSE
if(fromscratch){
  #Here we use spacy to extract verbs from the sentences
  p_load("spacyr")
  spacyr::spacy_install() 
  spacy_initialize(model = "en_core_web_sm") # if this initially doesn't work, try the previous spacy_install command and restart R.

@@

#wordnet rdf (in tripple format)
#wordnet rdf (in tripple format)

@@

verbs_sentence_wordnet <- verbs_sentence %>% left_join(wordnet_verbs)
#this is all possible matching glosses per ICBe sentence
#dim(verbs_sentence_wordnet) #227,426

@@

```{r}
 # py_install("tqdm")
 # py_install("pandas")
 # py_install("transformers")
 # py_install("torch")
 # py_install("sentence_transformers")
```

@@

# can install python packages in R using code chunk above
import torch
use_cuda = torch.cuda.is_available()
if use_cuda:
    print('__CUDNN VERSION:', torch.backends.cudnn.version())
    print('__Number CUDA Devices:', torch.cuda.device_count())
    print('__CUDA Device Name:',torch.cuda.get_device_name(0))
    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(0).total_memory/1e9)
#    print('__CUDA Device Name:',torch.cuda.get_device_name(1))
#    print('__CUDA Device Total Memory [GB]:',torch.cuda.get_device_properties(1).total_memory/1e9)    
import random
import os
from tqdm.auto import tqdm
import pandas as pd
from transformers import pipeline
from transformers.pipelines.pt_utils import KeyDataset
from sentence_transformers import SentenceTransformer
import numpy as np
glosses=np.array(r.gloss_unique) #sentences_unique_sanitized
glosses_chars = np.array([len(q) for q in glosses])
#sentences=sentences[sentence_chars<1000] #cull anything with too many characters
len(glosses) #4977
n=len(glosses)
chunk_length=100
n_chunks = int(np.ceil(n/chunk_length)) #can only 
glosses_chunks=[glosses[i:i + chunk_length] for i in range(0, n, chunk_length)]
len(glosses_chunks)
len(glosses_chunks[0])  
model = SentenceTransformer('paraphrase-mpnet-base-v2')
glosses_embeddings = np.vstack([model.encode(q) for q in glosses_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
glosses_embeddings.shape #(4977, 768)

```{python embed sentences for wordnet, echo=F, results='hide', message=F, warning=F, eval=T , cache=F}

#Make sure you have a gpu if you want to run this

@@

from sentence_transformers import SentenceTransformer
import numpy as np
sentences=np.array(r.sentences_unique) #sentences_unique_sanitized
sentence_chars = np.array([len(q) for q in sentences])
#sentences=sentences[sentence_chars<1000] #cull anything with too many characters
len(sentences) #12161 12162
n=len(sentences)
chunk_length=100
n_chunks = int(np.ceil(n/chunk_length)) #can only 
sentences_chunks=[sentences[i:i + chunk_length] for i in range(0, n, chunk_length)]
len(sentences_chunks)
len(sentences_chunks[0])  
#model = SentenceTransformer('sentence-transformers/all-mpnet-base-v2')
#model = SentenceTransformer('sentence-transformers/gtr-t5-xxl')
#model = SentenceTransformer('sentence-transformers/gtr-t5-xl')
model = SentenceTransformer('paraphrase-mpnet-base-v2')
#sentences
#sentences_test=['That is a happy person','That is a happy dog','That is a not happy person','That person is happy','This person is happy']
#temp = model.encode(sentences_chunks[0])
sentences_embeddings = np.vstack([model.encode(q) for q in sentences_chunks])  #[0:100] #cpu is possible just painfully slow #, device='0'
sentences_embeddings.shape #(12103, 768)

@@

  # py$sentences
  # py$glosses
  glosses_embeddings <- py$glosses_embeddings
  sentences_embeddings <- py$sentences_embeddings

@@

  condition_glosses_embeddings <- verbs_sentence_wordnet$gloss %in% rownames(glosses_embeddings)
  table(condition_glosses_embeddings) #there are 130 glosses that aren't in there
  gloss_clean <- verbs_sentence_wordnet$gloss
  gloss_clean[!condition_glosses_embeddings] <- rownames(glosses_embeddings)[1] #
  glosses_embeddings_expanded <- glosses_embeddings[gloss_clean ,]
  dim(glosses_embeddings_expanded)

  condition_sentences_embeddings <- verbs_sentence_wordnet$sentence %in% rownames(sentences_embeddings)
  table(condition_sentences_embeddings) #all are in it
  sentences_clean <- verbs_sentence_wordnet$sentence
  sentences_clean[!condition_sentences_embeddings] <- rownames(sentences_embeddings)[1] #
  sentences_embeddings_expanded <- sentences_embeddings[sentences_clean ,]
  dim(sentences_embeddings_expanded)

  verbs_sentence_wordnet$distances <- rowSums((glosses_embeddings_expanded-sentences_embeddings_expanded)^2)
  verbs_sentence_wordnet <- verbs_sentence_wordnet %>% arrange(crisno, sentence_number_int_aligned, token_id, distances)
  verbs_sentence_wordnet %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/verbs_sentence_wordnet.Rds"))

@@

        #bg( j = condition, part = "body", bg = "#EFEFEF") %>%
        #width(j = 1, width=1.25) %>%
        #width(j = 2:ncol(lit_review_clean), width=0.25) %>%
        flextable::fontsize(size = 6, part = "all") %>% 
        #rotate(rotation="tbrl",part="header") %>%
        set_header_labels( values = list(lemma = "lemma", wordnetid = "wordnetid", gloss="gloss", n="uses")) %>%
        #align(align = "center", part = "body") %>%
        #align(align = "center", part = "header") %>%
        flextable::padding(padding = 0, part = "all") %>%
        flextable::line_spacing(space = 1, part = "body") %>%
        #ftExtra::colformat_md(j = 1, part="body")   #Make sure this goes last or it'll get overwritten by the colformat above
        #fit_to_width(max_width=12) #This is slow
        #flextable::autofit() 
        #set_table_properties(width = 1, layout = "autofit")

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75, fig.width=6, fig.height=6}
  means_group_any <- codings_long_agreement %>% filter(value_normalized!='') %>% 
                     #filter(votes_total>1) %>% #
                     group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
                     dplyr::select(Experts=percent_expert,Novices=percent_novice) %>% summarise_all(mean)

@@

  means_keap <- codings_long_agreement %>% 
                #Algo 1 agreement
                filter(algo1==1) %>% 
                #This is top 1 agreement
                filter(value_normalized!='') %>% group_by(crisno,sentence_number_int_aligned, varname_normalized) %>% arrange(desc(percent_expert)) %>% filter(row_number()==1) %>% ungroup() %>% 
                group_by(varname_normalized) %>%
                #filter(votes_total>1) %>% 
                #filter(selected_by_experts>=1) %>%
                dplyr::select(Experts_keep=percent_expert,Novices_keep=percent_novice) %>% summarise_all(mean, na.rm=T)

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_percent_chose_tag_by_concept.png'), 
                  plot = p_percent_chose_tag_by_concept, width=8, height=8)
```

@@

  raterconfidence <- icb_long_clean %>% filter(email_id %>% str_detect('expert') & varname_normalized=='raterconfidence' ) %>%
                     dplyr::select(email_id, crisno, sentence_number_int_aligned, raterconfidence=value_normalized) %>% distinct()

@@

  ggplot2::ggsave(file=paste0(here::here(), '/replication_paper/psrm_draft/p_percent_chose_tag_by_confidence.png'), 
                  plot = p_percent_chose_tag_by_confidence, width=8, height=6)

@@

```{r}
rm(list = ls())
gc() 
#.rs.restartR()
```

# Recall

## Synthetic Narratives

\doublespacing

@@

```{r, eval=T}

paste0(here::here(), '/replication_data/out/case_study_cuban.Rds')

# cuba_recall <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1NuRWFB1HEbQbJu_JoEzJ9WYk7kfwwCryF7wBfKPT6uc/edit?usp=sharing", 
#                                 sheet="final") %>% janitor::clean_names() 
# cuba_recall  %>% saveRDS(paste0(here::here(), '/replication_data/out/case_study_cuban.Rds'))
cuba_recall <- readRDS(paste0(here::here(), '/replication_data/out/case_study_cuban.Rds'))

# replace_emoticons_cuba <- function(x){
#   x %>% str_replace_all('\U0001f1e8\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q241.png) ")) %>%
#         #https://emojiterra.com/flag-for-united-states/
#         str_replace_all('\U0001f1fa\U0001f1f8',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q30.png) ")) %>%
#         #https://emojiterra.com/flag-for-russia/
#         str_replace_all('\U0001f1f7\U0001f1fa',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q15180.png) ")) %>% 
#         #Turkey
#         str_replace_all('\U0001f1f9\U0001f1f7',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q43.png) ")) %>% 
#         #U.N.
#         str_replace_all('\U0001f1fa\U0001f1f3',  paste0(" ![](", here::here(), "/replication_data/in/flags_small//Q1065.png) "))
# }

ft_cuba_recall<- cuba_recall %>% 
                            dplyr::select(date, event, documents, icb_narrative, icbe=ic_be, icb, mids, phoenix_2)  %>%
                            #mutate(event = event %>% replace_emoticons_cuba() ) %>%
                            flextable::as_flextable() %>%
                            flextable::set_header_labels(values =
                            list(
                                  event = "Event",
                                  documents = "Mentions",
                                  icb_narrative = "ICB Narrative",
                                  icbe = "ICBe",
                                  icb = "ICB",
                                  mids="MIDs",
                                  phoenix_2="Phoenix"
                                 ) ) %>%
                            flextable::width( j = 1, width=0.25)  %>% 
                            flextable::width( j =2, width=2.0)  %>% 
                            #flextable::width( j = 3, width=.3)  %>% 
                            #flextable::width( j = 4, width=.3)  %>% 
                            #flextable::width( j = 5, width=.25)  %>% 
                            flextable::width( j = 6:8, width=2.0)  %>% 
                            #flextable::width( j = 6, width=1)  %>%
                            #flextable::width( j = 7, width=1.2)  %>% 
                            #flextable::width( j = 8, width=2)  %>% 
                            flextable::fontsize(size = 7, part = "all") %>%
                            #valign(j = 1:3, valign = "top", part = "body") %>%
                            flextable::line_spacing( space = 1.0, part = "all") %>% 
                            padding( padding = 1, part = "all") %>% 
                            bg( i = which( (1:nrow(cuba_recall) %% 2)==1   ) , part = "body", bg = "#EFEFEF") %>% #, j=1:3
                            ftExtra::colformat_md(j = 2, part="body")

@@

```{r, eval=T}
